Texture Mapping 3D Models of Indoor Environments with Noisy Camera Poses

### 2014-03-31 spie2014/spie2014.tex
old cleanup

For the purposes of texturing, it is convenient to treat each region
as planar, and fit a plane to each region. This plane corresponds to
the largest contiguous section of coplanar triangles in the region, as
most regions are characterized by small outcroppings from a largely
planar surface, such as objects on a table or features protruding from
a wall. The 3D surface composing a region is then projected onto its
calculated plane, and the resulting 2D planar polygon is used as the
texturing surface. This 2D planar approximation provides a simple, yet
approximately accurate surface onto which images can be projected in
order to generate textures. However, 3D surfaces are still retained in
order to achieve accurate results when performing occlusion checks,
and of course are used to project the final textures upon. Each region
now has a set of triangles representing the original model geometry,
as well as a planar approximation. The task now is to generate a
texture for each region.

@@

\begin{figure}
  \centering \subfloat[][]{\includegraphics[width=0.33\textwidth,
    height=0.8in]{wall2_naive.jpg}}
  \subfloat[][]{\includegraphics[width=0.33\textwidth,
    height=0.8in]{wall2_naive_shift.jpg}}
  \subfloat[][]{\includegraphics[trim=1.2cm 0cm 0cm 0cm,
    clip=true,width=0.33\textwidth,
    height=0.8in]{wall2_cache_shift.jpg}}

  \centering \subfloat[][]{\includegraphics[width=0.33\textwidth,
    height=0.8in]{wall2_shortest_shift.pdf}}
  \subfloat[][]{\includegraphics[width=0.33\textwidth,
    height=0.8in]{wall2_cache_shift_blend.pdf}}
  \subfloat[][]{\includegraphics[width=0.33\textwidth,
    height=0.8in]{wall2_shortest_shift_blend.pdf}}

@@

In order to correctly texture surfaces, it is important to detect and
remove parts of image projections containing texture for occluding
surfaces. For instance, in Figure \ref{fig:occlusion}(a), an image
used to texture the orange target surface also contains part of a gray
occluding surface. We remove this incorrect texture by performing
ray-polygon intersection tests between the camera location and every
surface in our model except the target surface
\cite{rayintersection}. These intersection tests are performed repeatedly in a
recursive grid, until all occlusions are detected and corresponding
occluded texture is removed. Occlusion checking works entirely with
geometry, so by ensuring that images match geometry using
\ref{sec:geometryAlignment}'s alignment procedure, texture belonging
to other surfaces is accurately removed, as seen in Figure
\ref{fig:occlusion}(b) vs. \ref{fig:occlusion}(c).

@@

To find the subset of images that covers the plane with minimal cost,
we form a shortest path problem. This can be done because the
wide-angle cameras have full floor-to-ceiling coverage of walls, and
the backpack operator logically only moves horizontally. We thus are
only concerned with lateral coverage when working with wall
surfaces. We can therefore construct a horizontal Directed Acyclic
Graph (DAG) from the images, with edge costs defined by the SSD cost
function, and solve a simple shortest path problem to find an optimal
subset of images with which to texture the surface \cite{dijkstra}.

@@

The last row of $X$ and corresponding last entry of $\vec{a}$ are used
to constrain the problem, as without them, all computed gains would be
allowed to scale by any amount. To keep gains at reasonable values,
the final observation is used: $\Sigma G_i = N$, where $N$ is the
number of images. This has the effect of setting the average of all
gains to 1, and is represented by the final row of ones in $X$, and
the corresponding $N$ value in $\vec{a}$.

@@

\subsection{Runtime}
As mentioned earlier, our approach is quite efficient. The top wall in
Figure \ref{fig:indivPlanes}(a) is a single region, and its texture
was generated with 7543 $\times$ 776 pixels, spanning a 40 meter long
wall. Given 41000 input images in the dataset, a 2.8 GHz dual-core
machine takes under 30 seconds to choose 36 candidate images and
perform the full texturing process. The tile-caching approach takes a
similar amount of time as well, with the larger floor textures in
Figure \ref{fig:indivPlanes}(c) taking 5-10 minutes to generate.
While not real-time, our process is capable of generating fast updates
after changes in various parameters or modifications to input data,
and if integrated directly into a 3D modeling system, could provide
quick visual feedback as data is collected.

@@

In this paper, we have developed a method for texture mapping models
of indoor environments with noisy camera localization data. We are
able to refine image locations based on geometry references as well as
feature matching, while robustly handling environments with repeating
or sparse details. Using the tile-based mapping approach, we can
texture both large planar features as well as smaller, more complex
surfaces. We also implemented a shortest path texturing method that
produces seamless textures on planes where multiple head-on images are
available. Both of these approaches are highly modular, and easily
tunable for similar systems across multiple environments.

>>>>

For the purposes of texturing, it is convenient to treat each region
as planar, and fit a plane to each region. This plane corresponds to
the largest contiguous section of coplanar triangles in the region, as
most regions are characterized by small outcroppings from a largely
planar surface, such as objects on a table or features protruding from
a wall. The 3D surface composing a region is then projected onto its
calculated plane, and the resulting 2D planar polygon is used as the
texturing surface. This 2D planar approximation provides a simple, yet
approximately accurate surface onto which images can be projected in
order to generate textures. However, the original 3D surfaces are
still retained in order to achieve accurate results when performing
occlusion checks, and are used to project the final generated textures
upon for 3D visualization. Each region now has a set of triangles
representing the original model geometry, as well as a planar
approximation. The task now is to generate a texture for each region.

@@

\begin{figure}
  \centering \subfloat[][]{\includegraphics[width=0.4\textwidth,
    height=0.81in]{wall2_naive.jpg}} \hspace{0.4in}
  \subfloat[][]{\includegraphics[width=0.4\textwidth,
    height=0.81in]{wall2_naive_shift.jpg}}

  \centering \subfloat[][]{\includegraphics[trim=1.2cm 0cm 0cm 0cm,
    clip=true,width=0.4\textwidth,
    height=0.81in]{wall2_cache_shift.jpg}} \hspace{0.4in}
  \subfloat[][]{\includegraphics[width=0.4\textwidth,
    height=0.81in]{wall2_shortest_shift.pdf}}

  \centering \subfloat[][]{\includegraphics[width=0.4\textwidth,
    height=0.81in]{wall2_cache_shift_blend.pdf}} \hspace{0.4in}
  \subfloat[][]{\includegraphics[width=0.4\textwidth,
    height=0.81in]{wall2_shortest_shift_blend.pdf}}

@@

In order to correctly texture surfaces, it is important to detect and
remove parts of image projections containing texture for occluding
surfaces. For instance, in Figure \ref{fig:occlusion}(a), an image
used to texture the orange target surface also contains part of a gray
occluding surface. We remove this incorrect texture by performing
ray-polygon intersection tests between the camera location and every
other surface in our model \cite{rayintersection}. These intersection
tests are performed repeatedly in a recursive grid, until all
occlusions are detected and corresponding occluded texture is
removed. Occlusion checking works entirely with geometry, so by
ensuring that images match geometry using
\ref{sec:geometryAlignment}'s alignment procedure, texture belonging
to other surfaces is accurately removed, as seen in Figure
\ref{fig:occlusion}(b) vs. \ref{fig:occlusion}(c).

@@

To find the subset of images that covers the plane with minimal cost,
we form a shortest path problem. This can be done because the
wide-angle cameras have full floor-to-ceiling coverage of walls, and
the backpack operator logically only moves horizontally. We thus are
only concerned with lateral coverage when working with wall
surfaces. We first crop each image projection to be rectangular, while
maintaining full vertical coverage. This makes it easy to determine
which images overlap, and has the benefit of enforcing image
boundaries to be vertical and thus less noticeable, as vertical
boundaries will minimally intersect the typically rectangular features
in indoor environments. We then construct a horizontal Directed
Acyclic Graph (DAG) from the images, with edge costs defined by the
SSD cost function, and solve a simple shortest path problem to find an
optimal subset of images with which to texture the surface
\cite{dijkstra}.

@@

The last row of $X$ and corresponding last entry of $\vec{a}$ are used
to constrain the problem, as without them, all computed gains would be
allowed to scale by any amount. To keep gains at reasonable values,
the final observation is used: $\Sigma G_i = N$. This has the effect
of setting the average of all gains to 1, and is represented by the
final row of ones in $X$, and the corresponding $N$ value in
$\vec{a}$.

@@

\subsection{Runtime}
As mentioned earlier, our approach is quite efficient. The top wall in
Figure \ref{fig:indivPlanes}(a) is a single region, and its texture
was generated with 7543 $\times$ 776 pixels, spanning a 40 meter long
wall. Given 41000 input images in the dataset, a 2.8 GHz dual-core
machine takes under 30 seconds to choose 36 candidate images and
perform the full texturing process. The tile-caching approach takes a
similar amount of time as well, with the large floor textures in
Figure \ref{fig:indivPlanes}(c) taking 5-10 minutes to generate.
While not real-time, our process is capable of generating fast updates
after changes in various parameters or modifications to input data,
and if integrated directly into a 3D modeling system, could provide
quick visual feedback as data is collected.

@@

In this paper, we have developed a method for texture mapping models
of indoor environments with noisy camera localization data. We are
able to refine image locations based on geometry references as well as
feature matching, while robustly handling environments with repeating
or sparse details. Using the tile-based mapping approach, we can
texture both large planar features as well as smaller, more complex
surfaces. We also implemented a shortest path texturing method that
produces seamless textures on surfaces where multiple head-on images are
available. Both of these approaches are highly modular, and easily
tunable for similar systems across multiple environments.
